Datasheet for Project Gutenberg's 'Stream of Consciousness Literature

### 2024-04-24 paper/datasheet_project_gutenberg.qmd
final datasheet updates

	- Each instance is eponymously titled.

@@

	- There is no missing information from individual instance since all texts have been in the public domain for a while, thus all data is up-to-date.

>>>>

	- Each instance is eponymously labelled, for instance 'book ID' is labelled 'book_id'.

@@

	- There is no missing information from individual instances since all texts have been in the public domain for a while, thus all data is up-to-date.
